### 2010-12-19 docs/tex/review.tex
Simple update
Thesis slides first commit

\section{Introduction}
This chapter contains a discussion on the field of Evolutionary Computing and Artificial Life. Both of these field of computer science are inspired by the process of evolution as it happens in nature. The model presented in this thesis is also based on an evolutionary process existing in nature. This thesis is part of the field of Artificial Life, motivated by the work of Echo and other such simulated Complex Adaptive Systems. In addition to the model discussed in chapter \ref{chapter:model}, this thesis also put some effort in finding application for the evolutionary process of mimicry (chapter \ref{chapter:application}). Similar to evolutionary computation, we intend to apply the deceptive process of mimicry to solve a problem in computer science.

@@

\subsection{Echo}
\label{subsec:echo}
Echo is a class of simulation model for complex adaptive system, designed primarily for gedanken experiments rather than precise simulations. Echo provides, a of populations of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites. Each agent has simple capabilities - offense, defense, trading and mate selection - defined by a set of chromosomes. Even though these capabilities are simple and defined simply, they provide a rich set of variations illustrating the four kernel properties of complex adaptive systems described in section \ref{subsec:complex-adaptive-system}.

>>>>

\section{Introduction}
This chapter contains a discussion on the field of Evolutionary Computing and Artificial Life. Both of these field of computer science are inspired by the process of evolution as it happens in nature. The model presented in this thesis is also based on an evolutionary process existing in nature. This thesis is part of the field of Artificial Life, motivated by the work of Echo and other such simulated Complex Adaptive Systems. In addition to the model discussed in chapter \ref{chapter:model}, this thesis also put some effort in finding application for the evolutionary process of mimicry (chapter \ref{chapter:application}). Similar to evolutionary computation, we intend to apply the deceptive process to solve a problem in computer science.

@@

\subsection{Echo}
\label{subsec:echo}
Echo is a class of simulation model for complex adaptive system, designed primarily for gedanken experiments rather than precise simulations. Echo provides, a populations of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites. Each agent has simple capabilities - offense, defense, trading and mate selection - defined by a set of chromosomes. Even though these capabilities are simple and defined simply, they provide a rich set of variations illustrating the four kernel properties of complex adaptive systems described in section \ref{subsec:complex-adaptive-system}.
